### 2016-10-18 R/ITHIM.Rmd
Changed names of 2003 ATUS data files
Not sure how this happened, unless ATUS changed the name of the files.  I can;t find files with the old name *_0311.dat

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

@@

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 1.65)
ITHIM.default <- updateITHIM(ITHIM.default, "muNonTravel", 4)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)

@@

```{r readnewMETs, echo = TRUE, eval = FALSE, echo = FALSE}
cpsFile <- "~/GHI/data/ATUS/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

summaryFile <- "~/GHI/data/ATUS/atussum_0311.dat"
summary <- read.table(summaryFile, header=T, skip=0, sep=",")
metaDataColumns <- 1:24
summaryList <- list(Data = summary[,-metaDataColumns], metaData = summary[,metaDataColumns])

@@

## Example (Bay Area)

First we define the baseline and scenario objects.

```{r instantiate, eval = FALSE, echo = FALSE}
ITHIM.baseline <- createITHIM(vision = "baseline", region = "SFBayArea")
ITHIM.scenario <- createITHIM(vision = "scenario", region = "SFBayArea")
```

Next we compare the scenario to the baseline using compareModels().

```{r RRs, eval = FALSE, echo = FALSE}
comparativeRisk <- compareModels(ITHIM.baseline,ITHIM.scenario)
```

### Deaths
```{r show, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$dproj.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### DALY
```{r show2, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$daly.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLD
```{r show3, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$yld.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLL
```{r show4, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$yll.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```

@@

```{r instantiate2, eval = FALSE, echo = FALSE}
ITHIM.baseline <- createITHIM(vision = "baseline", region = "national")
ITHIM.scenario <- createITHIM(vision = "scenario", region = "national")
```

@@

summaryFile <- "~/GHI/data/ATUS/atussum_0311.dat" # ~/Box Documents/work/CoBenefits/MaggieShare/MET Analysis/AmerTimeUse/atussum_0311.dat

cpsFile <- "~/GHI/data/ATUS/atuscps_0311.dat" #~/Box Documents/work/CoBenefits/MaggieShare/MET Analysis/AmerTimeUse/atuscps_0311.dat

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
install("~/ITHIM/")
#install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

@@

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM()
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 1.65)
ITHIM.default <- updateITHIM(ITHIM.default, "muNonTravel", 4)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)

@@

```{r readnewMETs, echo = TRUE, eval = FALSE, echo = FALSE}
cpsFile <- "~/GHI/data/ATUS/atuscps_2003.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

summaryFile <- "~/GHI/data/ATUS/atussum_2003.dat"
summary <- read.table(summaryFile, header=T, skip=0, sep=",")
metaDataColumns <- 1:24
summaryList <- list(Data = summary[,-metaDataColumns], metaData = summary[,metaDataColumns])

@@

@@

```{r instantiate2, eval = FALSE, echo = FALSE}
ITHIM.baseline <- createITHIM()
ITHIM.scenario <- createITHIM()
```

@@

summaryFile <- "~/GHI/data/ATUS/atussum_2003.dat" # ~/Box Documents/work/CoBenefits/MaggieShare/MET Analysis/AmerTimeUse/atussum_2003.dat

cpsFile <- "~/GHI/data/ATUS/atuscps_2003.dat" #~/Box Documents/work/CoBenefits/MaggieShare/MET Analysis/AmerTimeUse/atuscps_2003.dat
